---
title: "flexdashboard"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
data("instacart")
```

would like to know the most popular 3 products ordered in alsles: `fresh fruits`, `ice cream ice`, `bread`, `soft drinks`, and `tea`, as well as their number of products ordered in each aisle. 

pointplot:  number of items orderd vs. items
boxplot: number of items ordered in each products in aisle vs. aisles
barchart: number of items ordered in aisle vs. aisles

Clean the data
```{r}
data_df = instacart %>% 
  filter(aisle %in% 
           c("fresh fruits", "ice cream ice", "bread", "soft drinks", "tea")) %>% 
  select(aisle, product_name) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(desc(n))
```

scatterplot
```{r}
data_df %>% 
  mutate(product_name = fct_reorder(product_name, n)) %>% 
  plot_ly(x = ~product_name, y = ~n, type = "scatter", mode = "marker")
```

boxplot
```{r}

```

barchart
```{r}

```

