---
title: "flexdashboard"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
data("instacart")
```

I would like to know the most popular products ordered in aisles: `fresh fruits`, `ice cream ice`, `bread`, `soft drinks`, `tea`, and `asian foods` as well as their number of products ordered in each aisle. 

I also want to know the most frequently purchased items in each aisles (1 < average reorder day < 3), so I can try some popular items next time.

pointplot:  number of the most popular 3 items ordered vs. items' names
boxplot: number of items ordered in the most popular 10 products in aisle vs. aisles
barchart: days since prior order vs. items' names

Clean the data
```{r}
data_df = instacart %>% 
  filter(aisle %in% 
           c("fresh fruits", "ice cream ice", "bread", "soft drinks", "tea", "asian foods")) %>% 
  select(aisle, product_name, days_since_prior_order)
```

scatterplot
```{r}
data_df %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(desc(n)) %>% 
  ungroup() %>% 
  mutate(product_name = fct_reorder(product_name, n)) %>% 
  plot_ly( y = ~n, x = ~product_name, type = "scatter", mode = "marker") %>% 
  layout( xaxis = list(tickfont = list(size = 8)),
          yaxis = list(tickfont = list(size = 8)) )
```

boxplot
```{r}
data_df %>% 
  filter(aisle %in% 
           c("ice cream ice", "soft drinks", "tea", "bread", "asian foods")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 11) %>% 
  arrange(desc(n)) %>% 
  ungroup() %>% 
  mutate(product_name = fct_reorder(product_name, n)) %>% 
  plot_ly(
    y = ~n, x = ~aisle, color = ~aisle,
    type = "box", colors = "viridis")
```

barchart
```{r}
data_df %>% 
  filter(aisle %in% 
           c("ice cream ice", "soft drinks", "tea", "bread", "asian foods")) %>% 
  group_by(product_name) %>% 
  mutate(days_since_prior_order = mean(days_since_prior_order)) %>% 
  filter(days_since_prior_order > 1 & days_since_prior_order < 3) %>% 
  ungroup() %>% 
  mutate(product_name = fct_reorder(product_name, days_since_prior_order)) %>% 
  plot_ly(x = ~product_name, y = ~days_since_prior_order, color = ~product_name, type = "bar", colors = "viridis") %>% 
  layout(showlegend = FALSE)

```

